Meta-analysis of fungicide application timing experiments for powdery mildew

### 2020-05-22 vignette/191115_PMMB_DataWrangling_PM.Rmd
Tidy up repository and remove unnesercary files

# insert new calculations into data
PM_MB_means <- replace_data(template_data = PM_MB_means, 
                            new_data = Goolhi_13_m, 
                            new_data_column = c("AUDPC_m", "AUDPC_sd", "AUDPS_m","AUDPS_sd","Y_Msquare", "Inc_Ms"),
                            filter_cols = c("trial_ref", "year", "location", "host_genotype", 
                                           "fungicide_ai", "dose_ai.ha","n_treatment"))

@@

# insert new calculations into data
PM_MB_means <- replace_data(template_data = PM_MB_means, 
                            new_data = MarysM_13_m, 
                            new_data_column = c("AUDPC_m", "AUDPC_sd", "AUDPS_m","AUDPS_sd","Y_Msquare", "Inc_Ms"),
                            filter_cols = c("trial_ref", "year", "location", "host_genotype", 
                                           "fungicide_ai", "dose_ai.ha","n_treatment"))

@@

# insert new calculations into data
PM_MB_means <- replace_data(template_data = PM_MB_means, 
                            new_data = Premer_13_m, 
                            new_data_column = c("AUDPC_m", "AUDPC_sd", "AUDPS_m","AUDPS_sd","Y_Msquare", "Inc_Ms"),
                            filter_cols = c("trial_ref", "year", "location", "host_genotype", 
                                           "fungicide_ai", "dose_ai.ha","n_treatment"))

@@

# insert new calculations into data
PM_MB_means <- replace_data(template_data = PM_MB_means, 
                            new_data = Millm_13_m, 
                            new_data_column = c("AUDPC_m", "AUDPC_sd", "AUDPS_m","AUDPS_sd","Y_Msquare", "Inc_Ms"),
                            filter_cols = c("trial_ref", "year", "location", "host_genotype", 
                                           "fungicide_ai", "dose_ai.ha","n_treatment"))

>>>>

# insert new calculations into data
PM_MB_means <- replace_data(template_data = PM_MB_means, 
                            new_data = Goolhi_13_m, 
                            new_data_column = c("planting_date","AUDPC_m", "AUDPC_sd", "AUDPS_m","AUDPS_sd","Y_Msquare", "Inc_Ms"),
                            filter_cols = c("trial_ref", "year", "location", "host_genotype", 
                                           "fungicide_ai", "dose_ai.ha","n_treatment"))

@@

# insert new calculations into data
PM_MB_means <- replace_data(template_data = PM_MB_means, 
                            new_data = MarysM_13_m, 
                            new_data_column = c("planting_date","AUDPC_m", "AUDPC_sd", "AUDPS_m","AUDPS_sd","Y_Msquare", "Inc_Ms"),
                            filter_cols = c("trial_ref", "year", "location", "host_genotype", 
                                           "fungicide_ai", "dose_ai.ha","n_treatment"))

@@

# insert new calculations into data
PM_MB_means <- replace_data(template_data = PM_MB_means, 
                            new_data = Premer_13_m, 
                            new_data_column = c("planting_date","AUDPC_m", "AUDPC_sd", "AUDPS_m","AUDPS_sd","Y_Msquare", "Inc_Ms"),
                            filter_cols = c("trial_ref", "year", "location", "host_genotype", 
                                           "fungicide_ai", "dose_ai.ha","n_treatment"))

@@

# insert new calculations into data
PM_MB_means <- replace_data(template_data = PM_MB_means, 
                            new_data = Millm_13_m, 
                            new_data_column = c("planting_date","AUDPC_m", "AUDPC_sd", "AUDPS_m","AUDPS_sd","Y_Msquare", "Inc_Ms"),
                            filter_cols = c("trial_ref", "year", "location", "host_genotype", 
                                           "fungicide_ai", "dose_ai.ha","n_treatment"))
